Pyro-Velocity

### 2024-07-15 nbs/about/contributing.qmd
nit(contributing): remove extra PR list element
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

@@

1. The pull request should include [pytest](https://docs.pytest.org/) tests and, 
   where relevant, [xdoctest](https://github.com/Erotemic/xdoctest) 
   [doctests](https://docs.python.org/3/library/doctest.html).
2. If the pull request adds functionality, the 
3. [Google-style docstrings](https://sphinxcontrib-napoleon.readthedocs.io/en/latest/example_google.html)
   and [docs](https://github.com/pinellolab/pyrovelocity/tree/main/nbs) should be updated.
5. The pull request should pass the CI execution for the primary supported python version (currently Python 3.10).

>>>>

::: {#nte-contributing .callout-note collapse=true title="Current state of the repository"}
Please note that pyrovelocity is still in the early stages of development.
The current state of the documentation and repository are not complete
with respect to the procedures for contributing outlined here; however,
we plan to respect them as we continue to develop the project.
:::

@@

1. The pull request should include [pytest](https://docs.pytest.org/) tests and, 
   where relevant, [xdoctest](https://github.com/Erotemic/xdoctest) 
   [doctests](https://docs.python.org/3/library/doctest.html).
1. If the pull request adds or significantly modifies functionality, the relevant
   [Google-style docstrings](https://sphinxcontrib-napoleon.readthedocs.io/en/latest/example_google.html)
   and [docs](https://github.com/pinellolab/pyrovelocity/tree/main/nbs) should likely be updated.
1. The pull request should pass the CI execution for the primary supported python version (currently Python 3.10).
